Including EW and mixed QCD-EW corrections into PDF fits

### 2020-07-21 paper/sec-results.tex
Added plots
Some work on Sect. 3

In this section we present a comparison of NLO QCD and NLO QCD+EW predictions for three different processes: DY lepton-pair production, top-pair production, and finally Z-boson (lepton-pair) production with non-zero transverse momentum at the LHC.

Our first aim is a technical one, namely to show the validity of the results reconstructed with the \textsc{PineAPPL} grids introduced in section~\ref{sec:pineappl} and to give a measure of accuracy that can be achieved with them.
The second aim is to quantify the size of the EW corrections for the setups defined by the experimental collaborations for the processes given below.

The following processes are either already part of PDF determinations (7 and \SI{8}{\tera\electronvolt}) in refs.~\cite{} or will likely be part of next-generation PDF fits (\SI{13}{\tera\electronvolt}).
We discuss,
\begin{itemize}
\item in section~\ref{sec:atlas-high-mass-dy}, ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Aad:2013iua}, measuring $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ for the lepton-pair invariant mass $M_{\ell \bar{\ell}} > \SI{116}{\giga\electronvolt}$,
\item in section~\ref{sec:cms-dy}, CMS DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Chatrchyan:2013tia}, measuring $\mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}}$ for six slices in the range $\SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt}$,
\item in section~\ref{sec:atlas-top-pair-production}, ATLAS top-pair production at \SI{8}{\tera\electronvolt} \cite{Aad:2015mbv}, measuring
\begin{itemize}
\item the transverse momentum of the reconstructed top, $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{T}^\mathrm{t}$,
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} y_\mathrm{t}$,
\item the invariant mass of the reconstructed top pair, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$, and
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$,
\end{itemize}
\item in section~\ref{sec:cms-transverse-momentum}, CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt} \cite{Sirunyan:2019bzr}, measuring $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{Z}$ for $p_\mathrm{Z} > \SI{20}{\giga\electronvolt}$.
\end{itemize}
We used the MC \texttt{mg5\_aMC@NLO}~\cite{} and the PDF set \texttt{NNPDF31\_as\_0118\_luxqed}~\cite{} to generate the predictions.
The chosen PDF set contains a photon PDF calculated from the LUXQED method~\cite{}.
For each process---except top-pair production, which has stable tops in the final state---we use a complex-mass scheme~\cite{} as described in ref.~\cite{}.
The values of the most important parameters are
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} &= \SI{90}{\giga\electronvolt} \text{,} \quad &
m_\mathrm{t} &= \SI{170}{\giga\electronvolt} \text{,} \\
\Gamma_\mathrm{W} &= \SI{2}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} &= \SI{2}{\giga\electronvolt} \text{,} &
G_\mu &= \text{.}
\end{aligned}
\end{equation}

@@

>>>>

In this section we demonstrate the capabilities of \textsc{PineAPPL} by
computing fast interpolation grids, accurate to NLO QCD and NLO QCD+EW,
for a representative set of processes in which EW corrections are expected 
to be sizeable. In order to consider some realistic kinematics for these
processes, we resort to measurements commonly devised for inclusion in PDF
fits. Our aim is twofold. On the one hand, we want to validate the results
obtained with \textsc{PineAPPL}; on the other hand, we want to assess the
impact of the EW corrections for usual experimental setups. We describe first
the processes and measurements that we consider, then the computational
settings that we adopt, and finally the results that we obtain.

\subsection{Processes and measurements}
\label{subsec:processes_and_measurements}

We focus on the following three processes: DY lepton-pair production, top-quark
pair production, and Z-boson (lepton-pair) production with non-zero transverse
momentum at the LHC. For each of these processes, we consider the measurments
described below.

\paragraph{DY lepton pair production.}
We select the distribution, single-differential in the invariant mass of the
lepton pair, $M_{\ell \bar\ell}$, measured by the ATLAS experiment at a centre-of
mass energy of 7~TeV in the high-mass region
($M_{\ell\bar\ell}>116$~GeV)~\cite{Aad:2013iua}.
We also select the distribution, double-differential in the rapidity and in
the invariant mass of the lepton pair, $y_{\ell\bar\ell}$ and $M_{\ell\bar\ell}$,
measured by the CMS experiment at 7~TeV~\cite{Chatrchyan:2013tia}.
These measurements are currently included as standard in the
NNPDF3.1~\cite{Ball:2017nwa} and MMHT2014~\cite{Harland-Lang:2014zoa} PDF sets,
although with appropriate kinematic cuts that remove the bins at the largest
values of invariant mass, where EW corrections become sizeable.

\paragraph{Top-quark pair production.}
We select the distributions, single-differential in either the transverse
momentum of the top quark, $p_T^t$, or the invariant mass of the top-quark
pair, $m_{t\bar t}$, measured by the ATLAS and CMS experiments at a centre-of-mass
energy of 8~TeV~\cite{Aad:2015mbv,Khachatryan:2015oqa}. These measurements have
been extensively studied in the context of PDF fits in
Refs.~\cite{Czakon:2016olj,Bailey:2019yze,Amoroso:2020lgh,Kadir:2020yml}.
Because EW corrections are significantly smaller for distributions differential
in the rapidity of either the top quark or the top-quark
pair~\cite{Czakon:2017wor}, these were preferred for inclusion in the NNPDF3.1
set~\cite{Ball:2017nwa}.

\paragraph{$Z$-boson production with non-zero transverse momentum.}
We select the distribution, single-differential in the transverse momentum of
the $Z$ boson, $p_T^Z$, measured by the CMS experiment at a centre-of-mass
energy of 13~TeV~\cite{Sirunyan:2019bzr}. This measurement has not been
included in a PDF determination yet. Given that it has sub-percent
uncertainties, it is expected that EW corrections will be essential to
achieve a good description of it, and to constrain accurately the PDFs.
A similar challenge was observed in similar measurements, from the
ATLAS~\cite{Aad:2015auj} and CMS~\cite{Khachatryan:2015oaa} experiment at a
centre-of-mass energy of 8~TeV, in Ref.~\cite{Boughezal:2017nla}, which lead to
their partial inclusion (upon the selection of an appropriate kinematic cut)
in the NNDPF3.1 PDF set~\cite{Ball:2017nwa} and in variants of the CT18 PDF
set~\cite{Hou:2019efy}.

\subsection{Computational settings}
\label{subsec:computational_settings}

We discuss,
\begin{itemize}
\item in section~\ref{sec:atlas-high-mass-dy}, ATLAS high-mass DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Aad:2013iua}, measuring $\mathrm{d} \sigma / \mathrm{d} M_{\ell \bar{\ell}}$ for the lepton-pair invariant mass $M_{\ell \bar{\ell}} > \SI{116}{\giga\electronvolt}$,
\item in section~\ref{sec:cms-dy}, CMS DY lepton-pair production at \SI{7}{\tera\electronvolt} \cite{Chatrchyan:2013tia}, measuring $\mathrm{d} \sigma / \mathrm{d} y_{\ell \bar{\ell}}$ for six slices in the range $\SI{20}{\giga\electronvolt} < M_{\ell \bar{\ell}} < \SI{1500}{\giga\electronvolt}$,
\item in section~\ref{sec:atlas-top-pair-production}, ATLAS top-pair production at \SI{8}{\tera\electronvolt} \cite{Aad:2015mbv}, measuring
\begin{itemize}
\item the transverse momentum of the reconstructed top, $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{T}^\mathrm{t}$,
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} y_\mathrm{t}$,
\item the invariant mass of the reconstructed top pair, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$, and
\item its rapidity, $\mathrm{d} \sigma / \mathrm{d} M_{\mathrm{t} \bar{\mathrm{t}}}$,
\end{itemize}
\item in section~\ref{sec:cms-transverse-momentum}, CMS transverse momentum of the Z boson at \SI{13}{\tera\electronvolt} \cite{Sirunyan:2019bzr}, measuring $\mathrm{d} \sigma / \mathrm{d} p_\mathrm{Z}$ for $p_\mathrm{Z} > \SI{20}{\giga\electronvolt}$.
\end{itemize}
We used the MC \texttt{mg5\_aMC@NLO}~\cite{} and the PDF set \texttt{NNPDF31\_as\_0118\_luxqed}~\cite{} to generate the predictions.
The chosen PDF set contains a photon PDF calculated from the LUXQED method~\cite{}.
For each process---except top-pair production, which has stable tops in the final state---we use a complex-mass scheme~\cite{} as described in ref.~\cite{}.
The values of the most important parameters are
\begin{equation}
\begin{aligned}
M_\mathrm{W} &= \SI{80}{\giga\electronvolt} \text{,} \quad &
M_\mathrm{Z} &= \SI{90}{\giga\electronvolt} \text{,} \quad &
m_\mathrm{t} &= \SI{170}{\giga\electronvolt} \text{,} \\
\Gamma_\mathrm{W} &= \SI{2}{\giga\electronvolt} \text{,} &
\Gamma_\mathrm{Z} &= \SI{2}{\giga\electronvolt} \text{,} &
G_\mu &= \text{.}
\end{aligned}
\end{equation}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TPT}%
    \includegraphics[width=0.5\textwidth]{figures/pineappl_ATLAS_TTB_DIFF_8TEV_LJ_TTM}
    \caption{PineAPPL comparison for ATLAS top pair.}
    \label{fig:cmsdy2d11_bins56}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/pineappl_CMS_Z_13_TEV}
    \caption{PineAPPL comparison for CMS $Z$ $p_T$ distribution.}
    \label{fig:cmsdy2d11_bins56}
\end{figure}
